True versus apparent shapes of astrophysical bow shocks

### 2015-09-02 papers/Paper1/sec-conic.tex
Insert new figures and correct typographics errors
New figure for conic section

Where $q=\frac{R_0}{D}$ and $q' = \frac{R'_0}{D'}$
%Insert figures where needed

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "proplyd-bowshocks"
%%% End:

>>>>

Where $q=\frac{R_0}{D}$ and $q' = \frac{R'_0}{D'}$
\begin{figure}
\includegraphics[width=\linewidth]{conic2}
\label{fig:conic2}
\caption{Graphic example of the increasing of the projected radius of curvature with inclination}
\end{figure}

\begin{figure}
\includegraphics[width=\linewidth]{annotated}
\caption{Projected Radius of curvature vs projected $R_0$ for $\theta_c=60^\circ,45^\circ,28^\circ, 0^\circ,-15^\circ,-30^\circ$. Each colored points represent
the same shape at a different inclination. Being the dark blue the ones with the lower inclination and the red ones with the highest value. For closed shapes, there is
an assymptotic limit for the projected radius of curvature at high inclinations, while for open shapes there is an upper limit for inclination where a tangent line can be observed.}
\end{figure}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "proplyd-bowshocks"
%%% End:
